Validation failed EVT

### 2023-03-30 analysis/article-results.Rmd
Testing md addition

---
title: "Validation failed EVT"
author: "E. F. Bonneville"
date: "`r Sys.setenv(LANG = 'en_US.UTF-8'); format(Sys.Date(), '%d %B %Y')`"
output: 
  html_document:
    df_print: kable
    toc: yes
    toc_float: 
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries for knitting
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
library(DT)
```

@@

```{r inter-steyerberg}
# Second attempt in Ewout format 
# 
library(broom.helpers)
library(broom)

dev_unpen <- split(imps_combined |> 
                     filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  #broom::tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  #tidy_add_reference_rows(no_reference_row = all_categorical())
  mutate(
    "Development" = paste0(
      round(estimate, 3), " [",
      round(conf.low, 3), ", ",
      round(conf.high, 3), "]"
    )
  ) |> 
  select(term, Development)

>>>>

---
title: "Validation failed EVT"
author: "E. F. Bonneville"
date: "`r Sys.setenv(LANG = 'en_US.UTF-8'); format(Sys.Date(), '%d %B %Y')`"
output: 
  html_document:
    keep_md: true
    df_print: kable
    toc: yes
    toc_float: 
      smooth_scroll: false
editor_options: 
  chunk_output_type: console
---

@@

# Load libraries just for analysis rmd
library(ggplot2)
library(targets)
library(tidyverse)
library(tableone)
library(rms)
library(glmnet)
library(DT)
library(broom.helpers)
library(broom)
```

@@

```{r inter-steyerberg}
# Second attempt in Ewout format 
dev_unpen <- split(imps_combined |> 
                     filter(dataset == "develop"), ~ .imp) |> 
  map(.f = ~ glm(model_formula, family = binomial, data = .x)) |> 
  mice::pool() |> 
  #broom::tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  tidy(exponentiate = TRUE, conf.int = TRUE) |> 
  #tidy_add_reference_rows(no_reference_row = all_categorical())
  mutate(
    "Development" = paste0(
      round(estimate, 3), " [",
      round(conf.low, 3), ", ",
      round(conf.high, 3), "]"
    )
  ) |> 
  select(term, Development)
